---
title: "Harvard EDU S043 Final Project - Models"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: pdf
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

```{r}
#| label: libraries
#| echo: false

# Tidyverse
library(tidyverse)
# Haven; data interoperability, especially labelled data.
library(haven)
# Lme4
library(lme4)
```

```{r}
#| label: util

source("util.R")
```

### Load Data
```{r}
#| label: load-data

data <- readRDS("data/clean_data.rds") %>%
  drop_na(job_satis) %>%
  filter(add_count(., person_id)$n > 1) %>%
  mutate(
    job_satis = 4 - job_satis,
    # I like the idea of using a monotone coding or something, but with
    #  only three elements on the scale, I don't think it matters
    mismatch = mismatch %>% as_factor() %>% fct_recode(
      ":C" = "Closely related", ":S" = "Somewhat related", ":N" = "Not related"
    ),
    reason = reason_1_for_mismatch %>% as_factor() %>%
      fct_relevel("Logical Skip") %>%
      fct_recode(
        ":Pay" = "Pay, promotion opportunities",
        ":Conds" = "Working conditions",
        ":Loc" = "Job location",
        ":Change" = "Change in career or professional interests",
        ":Fam" = "Family-related reasons",
        ":Job" = "Job in highest degree field not available",
        ":Other" = "Other reason for not working",
        ":NA" = "Logical Skip"
      ),
    job_type = as_factor(job_type) %>% fct_recode(
      ":CS/M Prof" = "Postsecondary teachers-Computer and math sciences",
      ":CS/M" = "Computer scientists and mathematicians",
      ":BioMed Sci" = "Biological and medical scientists",
      ":Bio Prof" = "Postsecondary teachers-Life related sciences",
      ":Other Bio" = "Other life and related scientists",
      ":Chem" = "Chemists, except biochemists",
      ":Phys" = "Physicists and astronomers",
      ":Sci Prof" = "Postsecondary teachers-Physical and related sciences",
      ":Other Sci" = "Other physical and related scientists",
      ":Econ" = "Economists",
      ":Psych" = "Psychologists",
      ":Soc Prof" = "Postsecondary teachers-Social and related sciences",
      ":SocSci" = "Other social scientists",
      ":Other Eng" = "Other engineers",
      ":ChemE" = "Chemical engineers",
      ":CivE" = "Civil engineers",
      ":EE" = "Electrical or computer hardware engineers",
      ":MechE" = "Mechanical engineers",
      ":Eng Prof" = "Postsecondary teachers - engineering",
      ":Health" = "Health-related occupations",
      ":SciE Man" = "science and engineering managers",
      ":SciE Teach" = "Science and engineering pre-college teachers",
      ":SciE Teach2" = "Science and engineering pre-college teachers",
      ":Exec" = "Top and mid-level managers, executives, administrators",
      ":OtherMan" = "Other management related occupations",
      ":LibTeach" = "Non-science and engineering pre-college and post-secondary teachers",
      ":Other" = "Other Non-science and engineering occupations"
    ),
    job_type_group = as_factor(job_type_group) %>% 
      fct_relevel("Non-science and engineering occupations") %>%
      fct_recode(
        ":CS/M" = "Computer and mathematical scientists",
        ":LifeSci" = "Biological, agricultural and other life scientists",
        ":PhysSci" = "Physical and related scientists",
        ":SocSci" = "Social and related scientists",
        ":Eng" = "Engineers",
        ":STEM-adj" = "Science and engineering related occupations",
        ":Non-STEM" = "Non-science and engineering occupations",
        ":X" = "Logical Skip"
      ),
    major = as_factor(major) %>% fct_recode(
      ":CS/M" = "Computer and mathematical sciences",
      ":Bio" = "Biological sciences",
      ":LifeS" = "Other biological, agricultural, environmental life sciences",
      ":Chem" = "Chemistry, except biochemistry",
      ":Phys" = "Physics and astronomy",
      ":OtherSci" = "Other physical and related sciences",
      ":Econ" = "Economics",
      ":Poli" = "Political and related sciences",
      ":Psych" = "Psychology",
      ":Soc" = "Sociology and anthropology",
      ":OtherSoc" = "Other social sciences",
      ":ChemE" = "Chemical engineering",
      ":CivE" = "Civil engineering",
      ":EE" = "Electrical, electronics and communications engineering",
      ":MechE" = "Mechanical engineering",
      ":OtherE" = "Other engineering",
      ":Health" = "Health-related fields",
      ":OtherSci" = "Other science and engineering-related",
      ":Man" = "Management and administration",
      ":Non-STEM" = "Other non-science and engineering",
      ":X" = "Missing"
    ),
    major_group = as_factor(major_group) %>% 
      fct_relevel("Non-science and engineering fields") %>%
      fct_recode(
        ":CS/M" = "Computer and mathematical sciences",
        ":LifeSci" = "Biological, agricultural and environmental life sciences",
        ":PhysSci" = "Physical and related sciences",
        ":SocSci" = "Social and related sciences",
        ":Eng" = "Engineering",
        ":STEM-adj" = "Science and engineering-related fields",
        ":Non-STEM" = "Non-science and engineering fields",
        ":X" = "Missing"
      ),
    highest_degree = highest_degree %>% as_factor() %>% fct_recode(
      ":B" = "Bachelor's", ":M" = "Master's", ":Dr" = "Doctorate",
      ":Pr" = "Professional"
    ),
    # Salary: we treat the top and bottom 7.5% of the scale (for reasons)
    #  and then take a log2 centered around $60k, which is a round number close
    #  to the median. We could do ln around $66k but that would be harder to read.
    # We have to do the CPI conversion _after_ the cutoffs, as one cutoff is 
    #  the saturation of the scale. I don't _like_ this, but I can't think of
    #  much better.
    salary_adj = ifelse(
      test = salary < 150000 & salary > 20000, 
      yes = log2(salary * cpi_2009_conversion / 60000),
      no = 0  # We have to code this as zero or else a matrix is singular.
    ),
    rich = salary == 150000, # Upper end of the scale, 7.5% are saturated
    poor = salary <= 20000, # Bottom 7.5%; these data are anomalous
    # I'm centering this around 36 to 40 hours per week, as that's full time.
    weekly_hours = weekly_hours - 3,
    # We adjusted salaries to 2009, so let's adjust year to that too.
    # Nevermind, we don't have 2009 in the data, let's do the most recent one.
    survey_year = survey_year - 2013,
    # Our sample is mostly men (about 60%) so I'm setting them as the default
    gender = gender %>% as_factor() %>% fct_relevel("Male") %>%
      fct_recode(":M" = "Male", ":F" = "Female"),
    # Center around 25 (my age) and divide by 10 (decades, for scaling)
    age = (age - 25) / 10,
    # Our data is 65% white people
    race = race %>% as_factor() %>% fct_relevel("White") %>%
      fct_recode(":W" = "White", ":A" = "Asian", ":M" = "Under-represented minorities")
  ) %>%
  cache("data-lm-read.rds", use_cache = TRUE)
```

## Baseline

- how many respondents
- how many responded n times
- baseline characteristics (mean and % for each if applicable)
- job satis mean & stdev

```{r}
#| label: sample-size

data_unfiltered = readRDS("data/clean_data.rds")

# Raw Sample Size
nrow(data_unfiltered)

nrow(data_unfiltered %>% drop_na(job_satis))

nrow(data)
```

```{r}
#| label: baseline-characteristics


count(data, survey_year)
```

```{r}
#| label: baseline-measurements

salary_baseline = lmer(
  salary_adj ~ 1 +
    # Main covariate
    # mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/salary.rds", use_cache = FALSE)

salary_baseline_mixef <- lmer(
  salary_adj ~ 1 +
    # Main covariate
    # mismatch +
    # Education covariates
    highest_degree +
    # major_group +
    # Job covariates
    # job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + (1 | major) + (1 | job_type), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/salary_baseline_mixef.rds", use_cache = FALSE)

salary_job_test <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    salary_adj +
    (1 + salary_adj | job_type), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/salary_job_test.rds", use_cache = FALSE)

```

```{r}
library(ggplot2)
library(lme4)
library(dplyr)

# Assume 'fit' is your lmer object, 'data' is your dataframe

# 1️⃣ Fitted vs Observed
data <- data %>%
  mutate(fitted = predict(salary_job_test))

ggplot(data, aes(x = fitted, y = job_satis)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", color = "red") +
  labs(x = "Fitted values", y = "Observed job satisfaction")

# 2️⃣ Residuals plot
data <- data %>%
  mutate(resid = residuals(salary_job_test))

ggplot(data, aes(x = fitted, y = resid)) +
  geom_point(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted values", y = "Residuals")

# 3️⃣ Random effects (intercept and slope per job_type)
re <- ranef(salary_job_test)$job_type
re$job_type <- rownames(re)
ggplot(re, aes(x = `(Intercept)`, y = salary_adj, label = job_type)) +
  geom_point() +
  geom_text(nudge_y = 0.01, size = 3) +
  labs(x = "Random intercept", y = "Random slope for salary_adj")
```

```{r}

```

## Model 1: ANOVA, Fixed Effects

```{r}
#| label: nested-model

# Just the main covariate and grouping
model1 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Grouping
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model1.rds", use_cache = TRUE)

# Job covariates
model2 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    (1 | person_id), # Random intercept for each person
  data = data,
  # It _almost_ converges with the defaults
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model2.rds", use_cache = TRUE)

# Added demographic covariates
model3 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  # It _almost_ converges with the defaults
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model3.rds", use_cache = TRUE)

# Adding education covariates
model35 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model35.rds", use_cache = TRUE)

# Added job type
model4 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model4.rds", use_cache = TRUE)

# Added education covariates
model5 <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model5.rds", use_cache = TRUE)

see(model5) %>% write_csv("model5.csv")
```

```{r}
#|label: anova

anova(model1, model2, model3, model4, model5)
```

### Modeling Age 
```{r}
model_age <- lmer(
  job_satis ~ 1 +
    # Main covariate
    # mismatch +
    # Education covariates
    # highest_degree +
    # major_group +
    # Job covariates
    # job_type_group +
    # weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    # salary_adj +  # Log2, centered @ $60k, 2009 dollars
    # rich +  # Top 7.5% / $150k salary
    # poor +  # Bottom 7.5%
    # Demographic
    # gender +
    # age +  # Decades around 25 years
    # race +
    # survey_year +  # Centered around 2013
    (1 + age | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
)

see(model_age)
```

### Check Survey Year

```{r}
#| label: check-survey-year

model_no_survey_year = lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/model_no_survey_year", use_cache = TRUE)

anova(model_no_survey_year, model5)
```


## Model 2: Reasons
```{r}
#| label: reason-model
 
reason_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    reason +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  # It _almost_ converges with the defaults
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/reason_model.rds", use_cache = TRUE)

```


## Model 3: Job and Major Groups

```{r}
#| label: more-groups

groupless_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/groupless_model.rds", use_cache = TRUE)
 
groups_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + # Random intercept for each person
    (1 | major) +
    (1 | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/groups_model.rds", use_cache = TRUE)


anova(groupless_model, groups_model)

```

## Model 4: Does Salary Matter?

Yes, yes it does. But how does that change based on major?

```{r}
data <- data %>% mutate(
  salary_2009_trunc = ifelse(
      test = salary < 150000 & salary > 20000, 
      yes = salary * cpi_2009_conversion,
      no = NA
    ),
  ) %>%
  group_by(major) %>%
  mutate(average_2009_salary_for_major = mean(salary_2009_trunc, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    average_log2_salary_for_major = log2(average_2009_salary_for_major / 60000),
    salary_log2_major_centered = replace_na(log2(salary_2009_trunc / average_2009_salary_for_major), 0)
  )


centered_salary <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    average_log2_salary_for_major +  # Log2, centered @ $60k, 2009 dollars, average for major
    salary_log2_major_centered +  # Log2, centered 0 @ average for major, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + # Random intercept for each person
    (1 | major) +
    (1 | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/centered_salary.rds", use_cache = TRUE)


salary_slope <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    average_log2_salary_for_major +  # Log2, centered @ $60k, 2009 dollars, average for major
    salary_log2_major_centered +  # Log2, centered 0 @ average for major, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + # Random intercept for each person
    # I can't add random slopes for rich & poor here, as it makes it singular
    (1 + salary_log2_major_centered | major) +
    (1 | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/salary_interaction.rds", use_cache = TRUE)

anova(centered_salary, salary_slope)
```

## Main Model

```{r}
salary_job_slope <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + # Random intercept for each person
    # I can't add random slopes for rich & poor here, as it makes it singular
    (1 | major) +
    (1 + salary_adj | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/salary_job_slope.rds", use_cache = TRUE)

main_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    age:mismatch + # We want to see how the effect changes over time
    race +
    survey_year +  # Centered around 2013
    (1 | person_id) + # Random intercept for each person
    # I can't add random slopes for rich & poor here, as it makes it singular
    (1 + salary_adj | major) +
    (1 + salary_adj | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/main_model.rds", use_cache = TRUE)


main_model_ext <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    # Job covariates
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    age:mismatch + # We want to see how the effect changes over time
    race +
    survey_year +  # Centered around 2013
    (1 + salary_adj | person_id) + # Random intercept for each person
    # I can't add random slopes for rich & poor here, as it makes it singular
    (1 + salary_adj | major) +
    (1 + salary_adj | job_type),
  data = data,
  control = lmerControl(optimizer = "bobyqa")
  ) %>%
  cache("cache/main_model_ext.rds", use_cache = TRUE)



anova(model1, model2, model3, model35, salary_job_slope, main_model, main_model_ext)
```

## Model 5: Random Slope on Person

```{r}
# Added education covariates
person_slope_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 + salary_adj | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/person_slope_model", use_cache = TRUE)

# This takes an age and a half to run.
rand_pars_confints <-confint(person_slope_model, level = 0.99, parm = "theta_", method="profile") %>%
  cache("cache/salary_randpars_confint.rds", use_cache = TRUE)

  
rand_pars_confints
```


## Model 6: CLMM

```{r}
#| label: clmm

cl_data <- data %>%
  mutate(
    job_satis = as_factor(job_satis),
  )

model5_clmm <- ordinal::clmm(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = cl_data,
  link = "logit",
) %>% cache("cache/clmm_model.rds", use_cache = TRUE)
```

## Model 7: Over Time

```{r}
# Added education covariates
age_model <- lmer(
  job_satis ~ 1 +
    # Main covariate
    mismatch +
    # Education covariates
    highest_degree +
    major_group +
    # Job covariates
    job_type_group +
    weekly_hours +  # Centered around 36-40 hrs/wk
    # Pay covariates
    salary_adj +  # Log2, centered @ $60k, 2009 dollars
    rich +  # Top 7.5% / $150k salary
    poor +  # Bottom 7.5%
    # Demographic
    gender +
    age +  # Decades around 25 years
    mismatch:age +  # See if this changes
    race +
    survey_year +  # Centered around 2013
    (1 | person_id), # Random intercept for each person
  data = data,
  control = lmerControl(optimizer = "bobyqa")
) %>% cache("cache/age_model.rds", use_cache = FALSE)

anova(model5, age_model)
```