---
title: "Harvard EDU S043 Final Project - Plots"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: pdf
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

```{r}
#| label: load-data

# Tidyverse
library(tidyverse)
# Haven; data interoperability, especially labelled data.
library(haven)
# Lme4
library(lme4)

source("util.R")


data <- readRDS("data/clean_data.rds")
nrow(data)  # We expect 325883
```

Okay so we need a plot. A plot of what, though?

We should plot mismatch vs. job satisfaction; predicted and observed.

We can use this as a sensitivity analysis, depending on how many we have.

- Question: what's our average residual?


```{r}
#| label: load-and-predict
data <- readRDS("data-lm-read.rds") %>%
  mutate(
    major_group = factor(gsub("^:", "", as.character(major_group))),
    job_type_group = factor(gsub("^:", "", as.character(job_type_group)))
  )
```



```{r}
model5 <- readRDS("cache/model5.rds")
reason_model <- readRDS("cache/reason_model.rds")
main_model <- readRDS("cache/main_model.rds")

data <- data %>%
  mutate(
    # pred_model5 = predict(model5, data),
    # reason_pred = predict(reason_model, data)
    pred = predict(main_model, data)
  ) %>%
  relocate(starts_with("pred"), .after = mismatch)
```

```{r}
sqrt(mean((data$pred - data$job_satis) ** 2))
```

We need to somehow express something visually which uses mutli-level models !!

- make it very clear
- how are we showing variance in our model
- easiest: don't have them look at the technical report


## Plot Salary (x) v. Job Satis (y) v. Mismatch (f) 

facet per mismatch
salary on the x
job satisfaction on the y 
color/line is major or job type
scatter a few measurements or predictions in there

mismatch:salary
it would be cool to plot even

to plot a line with salary on x, it has to be a salary slope
- (1 + salary | job or major )

```{r}
binned <- data %>% 
  mutate(age_bin = cut(age, breaks = seq(0, max(age), by = 1), right = FALSE)) %>%
  drop_na(age_bin) %>%
  mutate(
    age_bin = droplevels(age_bin),
    mismatch = fct_relevel(mismatch, "close")
  )

levels(binned$age_bin) <- c(
  "15–24",   # first bin
  "25–34",   # second bin
  "35–44",   # etc.
  "45–54",
  "55–64"
)

binned %>% 
  filter(salary_adj != 0) %>%
  slice_sample(n = 1000, by = mismatch) %>%
  ggplot(aes(x = salary_adj, y = pred)) +
  geom_point(size = 0.5, alpha = 0.5) + 
  geom_smooth(data = binned, aes(color = age_bin), method = "lm") +
  facet_wrap(~mismatch) +
  scale_x_continuous(
    breaks = c(-1, 0, 1),
    labels = c("$30k", "$60k", "$120k")
  ) +
  labs(
    x = "Salary (2009 $USD)",
    y = "Job Satisfaction (Likert 0–3)",
    title = "Predicted Satisfaction by Mismatch, Salary, and Age",
    color = "Age"
  )

```

```{r}
#| label: bot-code
#| 
library(ggplot2)
library(dplyr)
library(tidyr)

# Make a grid for prediction
pred_grid <- expand.grid(
  salary_adj = seq(min(data$salary_adj), max(data$salary_adj), length.out = 100),
  age = c(25, 45, 65),
  mismatch = c("C", "S", "N")
)

pred_grid <- pred_grid %>%
  mutate(
    highest_degree = ":B",   # reference category
    weekly_hours = mean(data$weekly_hours, na.rm=TRUE),
    rich = FALSE,
    poor = FALSE,
    gender = FALSE,
    race = ":W",             # reference race
    survey_year = mean(data$survey_year, na.rm=TRUE),
    major = data$major[1],
    job_type = data$job_type[1],
    person_id = data$person_id[1]
  )

pred_grid$pred <- predict(main_model, newdata = pred_grid, re.form = NA)  # fixed effects only

ggplot() +
  # Observed density as scatter-like
  geom_density_2d(data = data, aes(x = salary_adj, y = job_satis), alpha = 0.3) +
  # Predicted lines
  # geom_line(data = pred_grid, aes(x = salary_adj, y = pred, color = factor(age)), size = 1.2) +
  facet_wrap(~mismatch) +
  # scale_color_manual(values = c("25"="blue","45"="green","65"="red")) +
  labs(
    x = "Salary Adjusted",
    y = "Job Satisfaction",
    color = "Age"
  ) +
  coord_cartesian(ylim = c(-0.5, 3.5)) +
  theme_minimal()
```

## Plot: Job + Major Effects

```{r}

effects <- ranef(main_model) %>% cache("cache/main_model_ranef.rds", use_cache=TRUE)
coefs = see(main_model)

main_intercept = coefs %>% filter(term == "(Intercept)") %>% getElement("estimate")
# major_corr = coefs %>% filter(term == "cor__(Intercept).salary_adj") %>% getElement("estimate")
# job_corr = coefs %>% filter(term == "(Intercept)") %>% getElement("estimate")

job_effects <- effects$job_type %>%
  as_tibble(rownames="name") %>%
  rename(intercept = "(Intercept)", slope = "salary_adj") %>%
  mutate(
    name = gsub("^:", "", name),
    type = "Jobs",
    intercept = intercept + main_intercept
  )

major_effects <- effects$major %>%
  as_tibble(rownames="name") %>%
  rename(intercept = "(Intercept)", slope = "salary_adj") %>%
  mutate(
    name = gsub("^:", "", name),
    type = "Majors",
    intercept = intercept + main_intercept
  )

vis_effects = bind_rows(job_effects, major_effects) %>%
  mutate(type = factor(type))

library(ggrepel)

vis_effects %>%
  ggplot(aes(x = intercept, y = slope, color = type)) +
  geom_smooth(method = "lm", se = FALSE, size = 0.7) +
  geom_point() +
  annotate("text", x = 2.52, y = -0.028, label = "ρ = -0.478") + 
  annotate("text", x = 2.48, y = 0.012, label = "ρ = 0.334") +
  geom_text_repel(aes(fill = type, label = name), box.padding = 0.2, max.overlaps = Inf) +
  labs(
    x = "Intercept / Average Satisfaction (Likert 0-3)",
    y = "Slope / Increase in Satisfaction (Likert 0-3) per Doubling Salary",
    title = "Satisfaction Slope/Intercept Relationship for Major and Job Type",
    color = "Key"
  ) +
  theme_minimal()
```


