---
title: "Harvard EDU S043 Final Project - Exploratory Analysis"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: html
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

# Workspace

This is setting up to use a virtual environment. It should print something like "The library is already synchronized with the lockfile.".

```{r}
#| label: virtual-env

renv::restore()
```

```{r}
#| label: libraries
#| echo: false

# Data Pliers; we use it for %>% and many other things
# see https://dplyr.tidyverse.org/authors.html for citation
library(dplyr)

# Haven; data interoperability, especially labelled data.
# see https://haven.tidyverse.org/authors.html for citation
# library(haven)
```

```{r}
#| label: load-data

data <- readRDS("data/clean_data.rds")
nrow(data)  # We expect 325883
```
## Notes about Data

I've cleaned and inspected the following columns. Here's an explanation of each and any notes about using them.

##### Outcomes

-   `jobsatis`: (ordinal, primary outcome, int 1-4 where 1 is good) job satisfaction

##### Groupers

-   `personid`: a unique identifier (string) for each person

##### Meta-Covariates

-   `survey_year`: (ordinal, originally `YEAR`)

##### Covariates

-   `mismatch`: (ordinal, primary covariate, originally `OCEDRLP`, int 1-3 where 3 is unrelated) how related their job is to their topic of highest degree.
-   `salary`: annual, and rounded to nearest thousand.
    -   many of them are missing
    -   a lot of them are too low (\$1000 a year?)
    -   The scale maxes at \$150k, and many of them have saturated that scale.
    -   People also tend to round to the nearest \$5k or \$10k.
    -   Maybe we take a log of salary and make an indicator variable for 'saturated'?
    -   Look into "tobit" modeling?
-   `major` (categorical, originally `NDGMED`)
    -   We also have `major_group` (originally `NDGMEMG`) which groups them coarser.
-   `highest_degree`: (categorical, originally `DGRDG`).
    -   We *cannot* code this as simply ordinal because #4 is a professional degree, which could be anywhere.

##### Demographic Covariates

-   `age`: (ranges from 23 to 75).
-   `birth_year`: (originally `BIRYR`, rounded down to nearest 5)
    -   Maybe we should center it (add 2.5)?
-   `gender`: (binary)
-   `minority`: (binary, originally `MINRTY`)
    -   Corresponds exactly to the under-represented `raceth` below.
-   `raceth`: Asian, white, under-represented, or other. "other" is not used.

##### Unused

-   `sample`: what survey they took; this is redundant in our dataset, as we are only using NSCG and we have the `survey_year` variable
-   `refid`: the same data as `personid` but used internally by the data. They wanted to remove the letters for some reason.

## Exploratory Data Analysis

-   Weight is important
-   make a histogram of the outcome; maybe with the primary covariate on one axis even
  - Treat it as continuous for now

```{r}
nrow(data)


data %>% filter(salary < 5000) %>% View
```

## Ideas

For ordinal covariates, we could use monotone coding. It seems like it adds a paramater which allows the scales to be spaced differently apart. For example, it might transform a Likert Scale (0, 1, 2) onto (0, 1.2, 3.5) because it seems like 1-2 is a more extreme gap than 0-1.

For linear-ish covariates which saturate (e.g. salary), we could use a tobit approach, which seems to add a parameter which estimates the chance of saturating. I'm not sure how it works.

For the ordinal outcome, we should use ordinal regression.

## Citations

-   Wickham H, François R, Henry L, Müller K, Vaughan D (2025). dplyr: A Grammar of Data Manipulation. R package version 1.1.4, https://dplyr.tidyverse.org.
-   Wickham H, Miller E, Smith D (2025). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.5.5, https://haven.tidyverse.org.
