---
title: "Harvard EDU S043 Final Project - Exploratory Analysis"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: pdf
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

# Workspace

This is setting up to use a virtual environment. It should print something like "The library is already synchronized with the lockfile.".

```{r}
#| label: virtual-env

renv::restore()
```

```{r}
#| label: libraries
#| echo: false

# Tidyverse
library(tidyverse)
# Haven; data interoperability, especially labelled data.
library(haven)
# Lme4
library(lme4)
```

```{r}
#| label: load-data

source("util.R")

data <- readRDS("data/clean_data.rds")
nrow(data)  # We expect 325883
```

## Exploratory Data Analysis

**To Do**
1. Unconditional Random Intercept Model
2. Conditional Random Intercept Model (with all covariates)
3. Use these two models to generate plots
  - We need to know if the models have to demonstrate clustering somehow.
  - We can make a heatmap of each of our groups; 27 x 20.
- We need to include average number of people per group
  - Our groups have _wildly_ different numbers of people in them
- How many people in the dataset? How many with `mismatch`?

There are 51834 datapoints in our sample which represent people without jobs.
They are missing `job_satis`, `job_type`, and so on— these people are not useful
to us, so we will drop them into space.
  
```{r}
#| label: drop-bums

data <- data %>% drop_na(job_satis)
```

Here's an idea: what if our groups are pairs of major and job type?

```{r}
#| label: make-pairs

data <- data %>%
  group_by(major, job_type) %>%
  mutate(pair_id = cur_group_id()) %>%
  ungroup()
```

### Plots
Let's do a basic plot to see what the odds 

```{r}
#| label: plot-satis-v-mismatch
#| eval: false

# Here we use the latest measurement for each person in our sample.
# I think the dataset is so large that this decision doesn't really matter.
data %>%
  filter(survey_year == 2013) %>%
  ggplot(aes(x = as_factor(mismatch), fill = as_factor(job_satis))) +
  geom_bar(position = "fill") +
  labs(
    x = "Percentage of Sample",
    y = "Relationship between Job and Degree",
    fill = "Job Satisfaction",
    title = "Job Satisfaction by Mismatch (2013)"
  ) + 
  scale_y_continuous(labels = scales::percent_format())
  
```

```{r}
#| label: plot-satis-v-reason
#| eval: false

data %>%
  filter(survey_year == 2013) %>%
  ggplot(aes(y = as_factor(reason_1_for_mismatch), fill = as_factor(job_satis))) +
  geom_bar(position = "fill") +
  labs(
    x = "Reason",
    y = "Percentage of Sample",
    fill = "Job Satisfaction",
    title = "Job Satisfaction by Reason"
  ) + 
  scale_x_continuous(labels = scales::percent_format())

```

### ICC 

Okay, let's take a look at the ICC.

```{r}
#| label: icc-pairs
#| eval: false

model <- cache(
  expression = lmer(job_satis ~ (1 | person_id) + (1 | pair_id), data = data),
  cache_file = "cache/pairs_unconditional_model.rds",
  use_cache = TRUE
)

get_variance(model) / sum(get_variance(model))
```


```{r}
#| label: icc-pairs-2013
#| eval: false

model <- cache(
  expression = lmer(job_satis ~ (1 | pair_id), data = data %>% filter(survey_year == 2013)),
  cache_file = "cache/unconditional_pairs_2013.rds",
  use_cache = TRUE
)

vars <- get_variance(model)
vars / sum(vars)
```

### Basic Model

```{r}
#| label: lm-data-prep

# Let's make our factors nicer
lm_data <- data %>%
  mutate(
    job_satis = 4 - job_satis,
    # I like the idea of using a monotone coding or something, but with
    #  only three elements on the scale, I don't think it matters
    mismatch = mismatch %>% as_factor() %>% fct_recode(
      ":C" = "Closely related", ":S" = "Somewhat related", ":N" = "Not related"
    ),
    reason = reason_1_for_mismatch %>% as_factor() %>%
      fct_relevel("Logical Skip") %>%
      fct_recode(
        ":Pay" = "Pay, promotion opportunities",
        ":Conds" = "Working conditions",
        ":Loc" = "Job location",
        ":Change" = "Change in career or professional interests",
        ":Fam" = "Family-related reasons",
        ":Job" = "Job in highest degree field not available",
        ":Other" = "Other reason for not working",
        ":NA" = "Logical Skip"
      ),
    highest_degree = highest_degree %>% as_factor() %>% fct_recode(
      ":B" = "Bachelor's", ":M" = "Master's", ":Dr" = "Doctorate",
      ":Pr" = "Professional"
    ),
    # Salary: we treat the top and bottom 7.5% of the scale (for reasons)
    #  and then take a log2 centered around $60k, which is a round number close
    #  to the median. We could do ln around $66k but that would be harder to read.
    # We have to do the CPI conversion _after_ the cutoffs, as one cutoff is 
    #  the saturation of the scale. I don't _like_ this, but I can't think of
    #  much better.
    salary_adj = ifelse(
      test = salary < 150000 & salary > 20000, 
      yes = log2(salary * cpi_2009_conversion / 60000),
      no = 0  # We have to code this as zero or else a matrix is singular.
    ),
    rich = salary == 150000, # Upper end of the scale, 7.5% are saturated
    poor = salary <= 20000, # Bottom 7.5%; these data are anomalous
    # I'm centering this around 36 to 40 hours per week, as that's full time.
    weekly_hours - 3,
    # We adjusted salaries to 2009, so let's adjust year to that too.
    year = survey_year - 2009,
    # Our sample is mostly men (about 60%) so I'm setting them as the default
    gender = gender %>% as_factor() %>% fct_relevel("Male") %>%
      fct_recode(":M" = "Male", ":F" = "Female"),
    # Center around 25 (my age) and divide by 10 (decades, for scaling)
    age = (age - 25) / 10,
    # Our data is 65% white people
    race = race %>% as_factor() %>% fct_relevel("White") %>%
      fct_recode(":W" = "White", ":A" = "Asian", ":M" = "Under-represented minorities")
  )
```

```{r}
#| label: full-model
#| eval: false

model <- lmer(
  job_satis ~ 1 +
    # mismatch +
    reason +
    highest_degree +
    salary_adj +
    rich +
    poor +
    weekly_hours +  # Around 36 to 40 hrs/week
    year +  # Around 2009
    gender +
    # It might make more sense to do survey_year and birth_year, as 
    #  age = birth_year + survey_year roughly, and that's kind of a pain.
    age +
    race +
    (1 | person_id) +  # Random intercept for each person
    (1 | major) + 
    (1 | job_type),
    # I don't think this was a good idea.
    # (1 | pair_id), # Random intercept for each major + job type pair
  data = lm_data,
  # It _almost_ converges with the defaults
  control = lmerControl(optimizer = "bobyqa")
  ) %>% 
  cache("cache/model_full.rds", use_cache = FALSE)

stats <- tidy(model) %>%
  left_join(
    confint(model, level=0.99, method="Wald") %>% as_tibble(rownames = "term"),
    by = "term"
  )

```

```{r}
#| label: 2013-model
#| eval: false

model2013 <- lmer(
  job_satis ~ 1 +
    mismatch +
    # reason +
    highest_degree +
    salary_scaled +
    rich +
    poor +
    weekly_hours +
    gender +
    age +
    race +
    # (1 | person_id) +  # Random intercept for each person
    (1 | pair_id), # Random intercept for each major + job type pair
  data = lm_data %>% filter(survey_year == 2013)
)
```

```{r}
#| label: clmm-model

cl_data <- lm_data %>%
  mutate(
    job_satis = as_factor(job_satis),
  )

cl_model <- ordinal::clmm(
  job_satis ~ 1 +
    # mismatch +
    reason +
    highest_degree +
    # salary_adj +
    rich +
    poor +
    weekly_hours +  # Around 36 to 40 hrs/week
    # year +  # Around 2009
    gender +
    age +
    race +
    (1 | person_id),  # Random intercept for each person
    # (1 | major) + 
    # (1 | job_type),
  data = cl_data %>% sample_n(5000),
  link = "logit",
  ) %>% 
  cache("cache/model_full.rds", use_cache = FALSE)


cl_stats <- tidy(cl_model) %>%
  left_join(
    confint(cl_model, level=0.99, method="Wald") %>% as_tibble(rownames = "term"),
    by = "term"
  )
```

### More Plots

```{r}
#| label: peek-salary

lm_data %>%
  mutate(salary_scaled=ifelse(salary_scaled == 0, NA, salary_scaled)) %>%
  ggplot(aes(x = salary_scaled)) +
  geom_histogram(bins = 30)

```

```{r}
data.frame(
  x = rep(1:5, each=5),
  y = rep(1:5, times=5),
  value = rnorm(25)
  ) %>%
  ggplot() +
  geom_tile(aes(x, y, fill = value)) +
  scale_fill_gradient(low="white", high="red")
```


```{r}
#| label: residual-heatmap

pair_residuals <- ranef(model2013)$pair_id %>%
  rownames_to_column("pair_id") %>%
  mutate(pair_id = as.integer(pair_id)) %>%
  rename(residual = `(Intercept)`)

heatmap_data <- data %>%
  filter(survey_year == 2013) %>%
  group_by(pair_id) %>%
  select(job_type, major, mismatch, pair_id) %>%  # Do this first for speed
  left_join(pair_residuals, by = "pair_id") %>%
  mutate(
    mismatch_prop = mean(mismatch == 1),
    job_type = as_factor(job_type) %>% fct_recode(
      "CS/M Prof" = "Postsecondary teachers-Computer and math sciences",
      "CS/M" = "Computer scientists and mathematicians",
      "BioMed Sci" = "Biological and medical scientists",
      "Bio Prof" = "Postsecondary teachers-Life related sciences",
      "Other Bio" = "Other life and related scientists",
      "Chem" = "Chemists, except biochemists",
      "Phys" = "Physicists and astronomers",
      "Sci Prof" = "Postsecondary teachers-Physical and related sciences",
      "Other Sci" = "Other physical and related scientists",
      "Econ" = "Economists",
      "Psych" = "Psychologists",
      "Soc Prof" = "Postsecondary teachers-Social and related sciences",
      "SocSci" = "Other social scientists",
      "Other Eng" = "Other engineers",
      "ChemE" = "Chemical engineers",
      "CivE" = "Civil engineers",
      "EE" = "Electrical or computer hardware engineers",
      "MechE" = "Mechanical engineers",
      "Eng Prof" = "Postsecondary teachers - engineering",
      "Health" = "Health-related occupations",
      "SciE Man" = "science and engineering managers",
      "SciE Teach" = "Science and engineering pre-college teachers",
      "SciE Teach2" = "Science and engineering pre-college teachers",
      "Exec" = "Top and mid-level managers, executives, administrators",
      "OtherMan" = "Other management related occupations",
      "LibTeach" = "Non-science and engineering pre-college and post-secondary teachers",
      "Other" = "Other Non-science and engineering occupations"
      ),
    major = as_factor(major) %>% fct_recode(
      "CS/M" = "Computer and mathematical sciences",
      "Bio" = "Biological sciences",
      "LifeS" = "Other biological, agricultural, environmental life sciences",
      "Chem" = "Chemistry, except biochemistry",
      "Phys" = "Physics and astronomy",
      "OtherSci" = "Other physical and related sciences",
      "Econ" = "Economics",
      "Poli" = "Political and related sciences",
      "Psych" = "Psychology",
      "Soc" = "Sociology and anthropology",
      "OtherSoc" = "Other social sciences",
      "ChemE" = "Chemical engineering",
      "CivE" = "Civil engineering",
      "EE" = "Electrical, electronics and communications engineering",
      "MechE" = "Mechanical engineering",
      "OtherE" = "Other engineering",
      "Health" = "Health-related fields",
      "OtherSci" = "Other science and engineering-related",
      "Man" = "Management and administration",
      "Non-STEM" = "Other non-science and engineering",
      "X" = "Missing"
    ),
  ) %>%
  add_count(name = "sample_size") %>%
  slice(1) %>%
  ungroup()
  

heatmap_data %>%
  ggplot(aes(x = job_type, y = major)) +
  geom_tile(aes(fill = residual)) +
  scale_fill_gradient2(low = "red", high = "green", midpoint = 0) +
  coord_fixed() +  # Make the pixels square
  geom_point(aes(color = 1 - mismatch_prop)) +
  scale_color_stepsn(
    colors = c(alpha("white", 0), alpha("blue", 0.5)),
    n.breaks = 6,
    limits = c(0.1, 0.9)
  ) +    # point colors
  # geom_text(aes(label = sample_size)) +
  labs(
    x = "Job Type",
    y = "Major (Highest Degree)",
    title = "Group Residuals",
    color = "%Match",
    fill = "Job Satis."
  ) +
  # Rotate X text
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Ideas

For ordinal covariates, we could use monotone coding. It seems like it adds a parameter which allows the scales to be spaced differently apart. For example, it might transform a Likert Scale (0, 1, 2) onto (0, 1.2, 3.5) because it seems like 1-2 is a more extreme gap than 0-1.

For linear-ish covariates which saturate (e.g. salary), we could use a tobit approach, which seems to add a parameter which estimates the chance of saturating. I'm not sure how it works.

For the ordinal outcome, we should use ordinal regression.

## Citations

```{r}
#| label: citations
#| exec: false

citation("tidyverse")
citation("lme4")
```

- Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V,
  Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” _Journal of Open Source Software_, *4*(43), 1686. doi:10.21105/joss.01686 <https://doi.org/10.21105/joss.01686>.
- Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of Statistical Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.

