---
title: "Harvard EDU S043 Final Project - Exploratory Analysis"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: html
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

# Workspace

This is setting up to use a virtual environment. It should print something like "The library is already synchronized with the lockfile.".

```{r}
#| label: virtual-env

renv::restore()
```

```{r}
#| label: libraries
#| echo: false

# Data Pliers; we use it for %>% and many other things
# see https://dplyr.tidyverse.org/authors.html for citation
library(dplyr)

# Haven; data interoperability, especially labelled data.
# see https://haven.tidyverse.org/authors.html for citation
# library(haven)
```

```{r}
#| label: load-data

data <- readRDS("data/ipums 2025-11-20.rds")
nrow(data)  # We expect 325883
```

## Data

### Data Cleaning

Let's rename columns so that they're easier to use.

```{r}
#| label: rename-and-reorder

names(data) <- tolower(names(data))

# Manual renames; I'm using tidyselect::any_of to make this idempotent
data <- data %>% rename(
  mismatch = any_of("ocedrlp"),
  survey_year = any_of("year"),
  birth_year = any_of("biryr"),
  minority = any_of("minrty"),
  highest_degree = any_of("dgrdg"),
  major = any_of("ndgmed"),
  major_group = any_of("ndgmemg"),
  recent_degree = any_of("mrdg"),  # categorical
  
  employment_status = any_of("lfstat"),  # categorical
  weekly_hours = any_of("hrswkgr"),  # ordinal, nullable
  job_type = any_of("nocpr"),  # categorical, nullable
  job_type_group = any_of("nocprmg"),  # categorical, nullable
  cpi_2009_conversion = any_of("cpi2009c"),  # continuous; multiply by salary to get 2009 dollars
  
  # Indicator varaibles
  # These are all categorical and very nullable
  reason_1_for_mismatch = any_of("nrrea"),
  reason_2_for_mismatch = any_of("nrsec"),
  reason_career_change = any_of("nrchg"),
  reason_conditions = any_of("nrcon"),
  reason_family = any_of("nrfam"),
  reason_location = any_of("nrloc"),
  reason_job_unavailable = any_of("nrocna"),
  reason_pay = any_of("nrpay"),
  reason_other = any_of("nrot"),
  
  satisfied_advancement = any_of("satadv"),
  satisfied_benefits = any_of("satben"),
  satisfied_challenge = any_of("satchal"),
  satisfied_independence = any_of("satind"),
  satisfied_location = any_of("satloc"),
  satisfied_responsibility = any_of("satresp"),
  satisfied_salary = any_of("satsal"),
  satisfied_security = any_of("satsec"),
  satisfied_contribution = any_of("satsoc"),
  
  technical_natural_science = any_of("mgrnat"),
  technical_other = any_of("mgroth"),
  technical_social_science = any_of("mgrsoc")
)

data <- data %>% relocate(
  # Outcome
  jobsatis,

  # Meta
  survey_year,
  cpi_2009_conversion,
  
  # Groupers
  personid,
  
  # Covariates
  mismatch,
  highest_degree,
  recent_degree,
  major,  # For highest degree, not recent
  major_group,  # For highest degree, not recent
  # missing: hg03y5, the year they graduated
  salary,
  employment_status,
  weekly_hours,
  job_type,
  job_type_group,
  
  # Demographic
  gender,
  age,
  birth_year,
  minority,
  raceth,
  
  # Secondary Outcomes/Covariates
  reason_1_for_mismatch,
  reason_2_for_mismatch,
  
  # Specific Indicators
  # These are probably not useful because we have reason_1 and reason_2
  reason_career_change,
  reason_conditions,
  reason_family,
  reason_location,
  reason_job_unavailable,
  reason_pay,
  reason_other,
  
  satisfied_advancement,
  satisfied_benefits,
  satisfied_challenge,
  satisfied_independence,
  satisfied_location,
  satisfied_responsibility,
  satisfied_salary,
  satisfied_security,
  satisfied_contribution,
  
  technical_natural_science,
  technical_other,
  technical_social_science,
  
  # Maybe unused
  weight,  # Not sure what this is
  cohort,  # First survey they took, not super interpretable
  srvmode,  # How they took the survey; we could try to do something fancy
  
  # Unused
  sample,  # See `survey_year`
  refid,  # See `personid`
  surid,  # Always 1 (NSCG)
  seqnum,  # Used internally by IPUMS
)

names(data)
```

A lot of the data has codes for "missing", "skip" or something similar which are not actually expressed as NA. Here I change that.

```{r}
#| label: missing-data

#' In a haven-labelled column, replace the values with the supplied label with
#' a tagged NA.
null_missing_codes <- function(column, label, tag) {
  # Here I change the labels to keep legibility
  attr(column, "labels")[label] <- haven::tagged_na(tag)
  
  # This won't work without the haven and dplyr functions, so I was explicit
  dplyr::if_else(haven::as_factor(column) == label, haven::tagged_na(tag), column)
}

# Replace "logical skip", "missing", "blank", etc. with NA
# Any column which is listed here has been inspected by me (Andrew)
# haven::zap_missing doesn't work here because we're not using tagged NAs.
data <- data %>% mutate(
  # Outcome
  jobsatis = null_missing_codes(jobsatis, label = "Logical Skip", tag = "s"),
  # Main Covariate
  mismatch = null_missing_codes(mismatch, label = "Logical Skip", tag = "s"),
  # Other Covariates
  salary = null_missing_codes(salary, label = "Logical Skip", tag = "s"),
  weekly_hours = null_missing_codes(weekly_hours, label = "Logical Skip", tag = "s"),
  job_type = null_missing_codes(job_type, label = "Logical Skip", tag = "s"),
  job_type_group = null_missing_codes(job_type_group, label = "Logical Skip", tag = "s")
)

```

The following columns did not have missing data: 

- `highest_degree`, `major` 
- `recent_degree` 
- `survey_year` 
- (demographic) `age`, `birth_year`, `gender`, `minority`, `raceth`.

```{r}
#| label: relabelling

```

### Details

I've cleaned and inspected the following columns. Here's an explanation of each and any notes about using them.

##### Outcomes

-   `jobsatis`: (ordinal, primary outcome, int 1-4 where 1 is good) job satisfaction

##### Groupers

-   `personid`: a unique identifier (string) for each person

##### Meta-Covariates

-   `survey_year`: (ordinal, originally `YEAR`)

##### Covariates

-   `mismatch`: (ordinal, primary covariate, originally `OCEDRLP`, int 1-3 where 3 is unrelated) how related their job is to their topic of highest degree.
-   `salary`: annual, and rounded to nearest thousand.
    -   many of them are missing
    -   a lot of them are too low (\$1000 a year?)
    -   The scale maxes at \$150k, and many of them have saturated that scale.
    -   People also tend to round to the nearest \$5k or \$10k.
    -   Maybe we take a log of salary and make an indicator variable for 'saturated'?
    -   Look into "tobit" modeling?
-   `major` (categorical, originally `NDGMED`)
    -   We also have `major_group` (originally `NDGMEMG`) which groups them coarser.
-   `highest_degree`: (categorical, originally `DGRDG`).
    -   We *cannot* code this as simply ordinal because #4 is a professional degree, which could be anywhere.

##### Demographic Covariates

-   `age`: (ranges from 23 to 75).
-   `birth_year`: (originally `BIRYR`, rounded down to nearest 5)
    -   Maybe we should center it (add 2.5)?
-   `gender`: (binary)
-   `minority`: (binary, originally `MINRTY`)
    -   Corresponds exactly to the under-represented `raceth` below.
-   `raceth`: Asian, white, under-represented, or other. "other" is not used.

##### Unused

-   `sample`: what survey they took; this is redundant in our dataset, as we are only using NSCG and we have the `survey_year` variable
-   `refid`: the same data as `personid` but used internally by the data. They wanted to remove the letters for some reason.

## Exploratory Data Analysis

-   Weight is important

```{r}
nrow(data)


data %>% filter(salary < 5000) %>% View
```

## Ideas

For ordinal covariates, we could use monotone coding. It seems like it adds a paramater which allows the scales to be spaced differently apart. For example, it might transform a Likert Scale (0, 1, 2) onto (0, 1.2, 3.5) because it seems like 1-2 is a more extreme gap than 0-1.

For linear-ish covariates which saturate (e.g. salary), we could use a tobit approach, which seems to add a parameter which estimates the chance of saturating. I'm not sure how it works.

For the ordinal outcome, we should use ordinal regression.

## Citations

-   Wickham H, François R, Henry L, Müller K, Vaughan D (2025). dplyr: A Grammar of Data Manipulation. R package version 1.1.4, https://dplyr.tidyverse.org.
-   Wickham H, Miller E, Smith D (2025). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.5.5, https://haven.tidyverse.org.
