---
title: "Harvard EDU S043 Final Project - Exploratory Analysis"
date: 2025-11-22
author:
  - name: Andrew Bogdan
  - name: Lin Jin
  - name: Livia Cheng
format: html
execute:
  # Use the knitr cache (https://quarto.org/docs/computations/caching.html#knitr-cache)
  cache: true
---

# Workspace

This is setting up to use a virtual environment. It should print something like "The library is already synchronized with the lockfile.".

```{r}
#| label: virtual-env

renv::restore()
```

```{r}
#| label: libraries
#| echo: false

# Tidyverse
library(tidyverse)

# Haven; data interoperability, especially labelled data.
# library(haven)
```

```{r}
#| label: load-data

data <- readRDS("data/clean_data.rds")
nrow(data)  # We expect 325883
```

## Exploratory Data Analysis

**To Do**

- Make a histogram of the distribution of the outcome.
  - Maybe relate it to the primary covariate.

```{r}
#| label: plot-satis-v-mismatch

# We could use tidyr for this
data %>%
  drop_na(job_satis) %>%
  drop_na(mismatch) %>%
  ggplot(aes(y = as_factor(mismatch), fill = as_factor(job_satis))) +
  geom_bar(position = "fill")
  
```

Let's try a basic model

```{r}
#| label: unconditional-random-intercept

library(lme4)

# TODO
```

```{r}
#| label: ICC


# TODO
```

## Ideas

For ordinal covariates, we could use monotone coding. It seems like it adds a paramater which allows the scales to be spaced differently apart. For example, it might transform a Likert Scale (0, 1, 2) onto (0, 1.2, 3.5) because it seems like 1-2 is a more extreme gap than 0-1.

For linear-ish covariates which saturate (e.g. salary), we could use a tobit approach, which seems to add a parameter which estimates the chance of saturating. I'm not sure how it works.

For the ordinal outcome, we should use ordinal regression.

## Citations

```{r}
#| label: citations
#| exec: false

citation("tidyverse")
```

- Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V,
  Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” _Journal of Open Source Software_, *4*(43), 1686. doi:10.21105/joss.01686 <https://doi.org/10.21105/joss.01686>.
